Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach

### 2016-06-01 introduction.tex
Reduce the seismicity part and remove the earthquakes.

\section{Introduction}
\noindent
\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs. Basically the visibility graph presents the connection between nodes in the network. For any time series, two characteristics are attributed to each incidents: ocurrance time and value of the incident. Two events are in connection or visible to each other, if no other event interrupts their linear connection. In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:

@@

\noindent
Northern Iran has an elaborate seismic history.  Having considerable number of earthquakes and also being in different tectonic seismic zone, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series. In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions. We also investigate the variation of $<T_C>$ value through time.

>>>>

\section{Introduction}
\noindent
\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs. Basically the visibility graph presents the connection between nodes in the network. For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other, if no other event interrupts their linear connection. In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:

@@

\noindent
Northern Iran has an elaborate seismic history.  Having considerable number of earthquakes and also being in different tectonic seismic region, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series. In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions. We also investigate the variation of $<T_C>$ value through time.

### 2016-06-01 seismicity.tex
Reduce the seismicity part and remove the earthquakes.

\noindent
Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. Here a series of historical earthquakes occurred within a time period of more than 1100 years. At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.  The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression. An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.

\noindent
There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest, as part of Azerbaijna tectonic seismic zone. The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.

The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 m; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF. Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879. Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}. Most recently, earthquakes with Mw 6.1 in 1997 and Mw 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.

The main Kopeh-Dagh fault system has experienced some historic earthquakes. Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of $Ms$ 7.2 in 1948 and destroyed more than 30 villages in Iran. This was the strongest earthquake to strike this region since at least 1455.
The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults striking about E - W \citep{Berberian2001}. \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km. 
Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.

>>>>

\noindent
Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression \citep{Berberian1999}.

\noindent
 The Tabriz region (located in Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
\noindent
The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults striking about E - W \citep{Berberian2001}. \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
